\documentclass[%
  reprint,
  aps,
  pra,
  superscriptaddress,
  a4paper
]{revtex4-2}

\usepackage{xcolor}
\usepackage{lipsum}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage[
  bookmarks=false,
  bookmarks=true,
  colorlinks,
  linkcolor=blue,
  urlcolor=blue,
  citecolor=blue,
  plainpages=false,
  pdfpagelabels,
  final,
  breaklinks=true
]{hyperref}
\hypersetup{
pdftitle={The Arthur BibTeX style file}, 
pdfauthor={Emilio Pisanty}
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\usepackage{natbib}
%% reduce spacing inside [1, 2]:
\makeatletter \def\NAT@def@citea{\def\@citea{\NAT@separator\,}} \makeatother
\newcommand{\citer}[1]{Ref.~\citealp{#1}}
\newcommand{\citers}[1]{Refs.~\citealp{#1}}


\newcommand{\reffig}[1]{Fig.~\ref{#1}}



\begin{document}



\title{The Arthur and Lancelot styles for BibTeX}

\author{Emilio Pisanty}
\email{emilio.pisanty@kcl.ac.uk}
\affiliation{Attosecond Quantum Physics Laboratory, Department of Physics, King's College London, Strand, WC2R 2LS London, UK}

\date{\today}

\begin{abstract}
This is a showcase file for the BibTeX style files \texttt{arthur.bst} and \texttt{lancelot.bst}.
\end{abstract}

\maketitle

The BibTeX style files \texttt{arthur.bst} and \texttt{lancelot.bst} are optimized for physics (more specifically atomic, molecular and optical physics). 
\texttt{arthur.bst} was generated from the \texttt{makebst} utility, and then modified by hand to give it DOI linking capabilities comparable to those used in production by modern physics journal.
\texttt{lancelot.bst} is a hand-modified version of \texttt{apsrev4-2.bst}.

Both style files admit arbitrary eprint capability for indicating the URL and identifier of the eprint,
\begin{verbatim}
  eprint = {https://arxiv.org/abs/yymm.nnnn},
  archive = {arXiv:yymm.nnnn},
\end{verbatim}
whether that be on arXiv or somewhere else, and they both have a dedicated \texttt{preprint} entry type:
\begin{verbatim}
@preprint{arxivPreprint,
  author = {Ann Author},
  title = {A preprint still under review},
  year = {2020},
  eprint = {https://arxiv.org/abs/yymm.nnnn},
  archive = {arXiv:yymm.nnnn},
}  
\end{verbatim}

The presend document exists to showcase how the style files behaves when typesetting a variety of references, including
journal articles~\cite{journalArticle, journalArticle2},
preprints~\cite{arxivPreprint}, 
books~\cite{bookExample}, 
theses~\cite{thesisExample}, 
code~\cite{codeExample}, and
collections~\cite{collectionExample}.
This repository also contains two shorter versions of the style file, \texttt{arthurShort.bst} and \texttt{arthurUltraShort.bst}, which produce minified entries.


The name `arthur' derives from the name of the `master' style form the \texttt{makebst} utility, \texttt{merlin.bst}, in the understanding that \texttt{arthur} is still learning from \texttt{merlin}.
The name `lancelot' was made to give `arthur' a friend.

On the whole, I am extremely happy with both this style files.
The original, \texttt{arthur}, have a minor `tick', in that it tends to hyperlink the period between a paper's title and its journal reference; this is a side effect of the DOI linker which I was unable to iron out. 
If this is found undesirable, it can be fixed using a simple Perl script; a sample `prettifier' shell file is provided.

The newer file, \texttt{lancelot}, does not suffer from this, and it is the one I (currently) prefer.

For some historical context, I prepared the style file \texttt{arthur} around 2015, before version 4.2 of the \texttt{revtex} package became widespread. 
The updated version of \texttt{revtex} does provide APS style files which include proper DOI hyperlinking, with the clearest contender being \texttt{apsrev4-2.bst}, and those may be found preferable depending on individual tastes; copies are easily found online, and they are natively available to \texttt{revtex4-2} documents. 
A copy of \texttt{apsrev4-2.bst} is included in this repository (under its LPPL license) for ease of comparison.
The newer homebrew, \texttt{lancelot.bst}, is a modification of the new-standard \texttt{revtex} to streamline the handling of preprints and arXiv (or other) eprint links.


%\bibliographystyle{apsrev4-2}
%\bibliographystyle{arthur}
\bibliographystyle{lancelot}
\bibliography{references}{}



\end{document}













